{{module}} Analysis

### 2024-03-18 templates/analysis-module-R/notebook-template.Rmd
Apply suggestions from code review
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

It is a good idea to start with a brief introduction to the analysis, including the purpose of the analysis, the data used, and the methods applied.
Replace this text with your own introduction, and be sure to update the `title` and `author` fields at the top of the document.

@@

Load required packages in the following chunk, if needed.
Do not install packages here, only load them with the `library()` function.

```{r packages}
# load required packages
# e.g. library("tidyverse")
```

@@

Setting paths to directories and files for input and output at the start of a notebook can be helpful for organization and reproducibility.
You may not know all of the paths you need when you start a notebook, but once you do, keeping them all in one place can be helpful, both for yourself in the future and for other users of the notebook.

@@

In the chunk below, we included some common directories that you might need, finding their locations using the very useful `rprojroot` package.

@@

Set paths to input and output directories and files in the chunk below

@@

# Output files
```

>>>>

It is a good idea to start with a brief introduction to the analysis, including the purpose of the analysis, the data used, and the methods applied.
Replace this text with your own introduction, and be sure to update the `title:` and `author:` fields in the YAML header at the top of the document.
Don't forget to rename this files as well!

@@

Load required packages in the following chunk, if needed.
Do not install packages here; only load them with the `library()` function.

```{r packages}
# load required packages
# e.g. library(tidyverse)
```

@@

Setting paths to directories and files for input and output at the start of a notebook can be helpful for organization and reproducibility.
You may not know all of the paths you need when you start a notebook, but once you do, keeping them all in one place is helpful, both for yourself in the future and for other users of the notebook.

@@

In the chunk below, we include some common directories that you might need, finding their locations using the very useful [`rprojroot` package](https://rprojroot.r-lib.org/).

@@

Set paths to input and output directories and files in the chunk below.

@@

# Output files

```
